Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2024-07-14 paper/si.tex
Updates from Overleaf
update from overleaf

\documentclass[9pt,twoside,lineno]{pnas-new-si}
% Use the lineno option to display guide line numbers if required.
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
\externaldocument{ms}
\templatetype{pnassupportinginfo}
\input{paper/macros}

@@

\section{Heading}

\ref{alg:mop}

\subsection*{Subhead}
Type or paste text here. You may break this section up into subheads as needed (e.g., one section on ``Materials'' and one on ``Methods'').

\subsection*{Materials}
Add a materials subsection if you need to.

\subsection*{Methods}
Add a methods subsection if you need to.

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=\textwidth]{example-image}
\caption{First figure}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{frog}
\caption{Second figure}
\end{figure}

\begin{table}\centering
\caption{This is a table}

\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}
\end{table}

%%% Add this line AFTER all your figures and tables
\FloatBarrier

\movie{Type legend for the movie here.}

\movie{Type legend for the other movie here. Adding longer text to show what happens, to decide on alignment and/or indentations.}

\movie{A third movie, just for kicks.}

\dataset{dataset_one.txt}{Type or paste legend here.}

\dataset{dataset_two.txt}{Type or paste legend here. Adding longer text to show what happens, to decide on alignment and/or indentations for multi-line or paragraph captions.}

\bibliography{pnas-sample}

>>>>

\documentclass[9pt,twoside,lineno]{pnas-new-si}

% Use the lineno option to display guide line numbers if required.
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
\externaldocument{ms}

\templatetype{pnassupportinginfo}
\input{macros}
\usepackage{refcount}

\setcounter{thm}{\getrefnumber{finalthm}}
\addtocounter{thm}{-1}

\setcounter{lem}{\getrefnumber{finallem}}
\addtocounter{lem}{-1}

\setcounter{defn}{\getrefnumber{finaldefn}}
\addtocounter{defn}{-1}

\setcounter{prop}{\getrefnumber{finalprop}}
\addtocounter{prop}{-1}

\setcounter{aspt}{\getrefnumber{finalaspt}}
\addtocounter{aspt}{-1}

@@

\section{MOP-$\alpha$ Functional Forms}

\label{appendix:functional}
\input{appendix/functional}

\section{Optimization Convergence Analysis}
\label{appendix:convergence}
\input{appendix/convergence}

\section{Feynman-Kac Models and Monte Carlo Approximations}
\label{appendix:feynman}
\input{appendix/feynman}

\section{A Strong Law of Large Numbers for Triangular Arrays of Particles With Off-Parameter Resampling}
\label{appendix:targeting}
\input{appendix/targeting}

\section{Consistency of Off-Parameter Resampled Gradient Estimates}
\label{appendix:consistency}
\input{appendix/consistency}

\section{Bias-Variance Analysis}
\label{appendix:biasvar}
\input{appendix/biasvar}

\section{Figures for Bayesian Inference}
\label{appendix:bayes}
\input{appendix/bayes}

%%% Each figure should be on its own page

\bibliography{paper/bib-ifad}
